On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-04 arity1.tex

\begin{enumerate}
	\item bead $i+1$ is fixed at $(2,1)$ and can bond with a bead at $(2,0)$. Now consider bead $i+2$. For $i+1$ to be fixed at $(2,1)$, $i+2$ needs to form a bond somewhere, otherwise $i+2$ could go to $(2,1)$ forming the bond with the bead at $(2,0)$ and there would be two conformations with the maximal $1$ bond. The only possibility is that there is a bead at $(3,0)$ and $i+2$ can bond with it when placed at $(3,1)$. We can apply the same argument inductively: there is some $m\geq 0$ such that grid points $(\ell,0)$ are occupied by active beads, for all $\ell\in \{2,\dots,2+m\}$, and there is no bead at $(3+m,0)$. Such an $m$ exists, and it is not greater than $n$. Then, bead $i+\ell$ is fixed at $(\ell+1,1)$ and bonds with $(\ell+1,0)$. However, bead $i+2+m$ cannot be fixed anywhere, because $i+2+m$ and $i+3+m$ can only add one bond to the conformation, and that is possible either with $i+2+m \rightarrow (2+m,1)$, $i+3+m \rightarrow (3+m,1)$ or with $i+2+m \rightarrow (2+m,2)$, $i+3+m \rightarrow (2+m,1)$. 
	\begin{figure}
		\centering
		\includegraphics[width=0.6\linewidth]{./Fig/hexagonOut2}
		\caption{}
		\label{fig:hexagonout2}
	\end{figure}

@@

\begin{figure}
	\centering
	%\includegraphics[width=0.3\linewidth]{./hexagonOut1}
	%\hspace{10mm} %
	\includegraphics[width=0.6\linewidth]{./Fig/hexagonOut3n}

@@

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (0.0, 1.732) -- (-0.5, 0.866);
        \draw [dashed] [red] (0.0, 1.732) -- (0.5, 0.866);
        \draw [dashed] [red] (0.0, 0.0) -- (-0.5, 0.866);
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \draw (0.0, 0.0) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (0.5, 0.866);
        \draw (0.0, 1.732) -- (0.5, 0.866);
        \draw [dashed] [red] (0.0, 0.0) -- (0.5, 0.866);
        \draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
      \end{tikzpicture}

    \end{tabular}
    \caption{}
    \label{fig:beadi}
  \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \begin{tabular}{ccc}
      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (2.0, 0.0) circle [radius = 0.1];
        \fill (3.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (1.5, 0.866) circle [radius = 0.1];
        \fill (2.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (1.5, 0.866);
        \draw (1.5, 0.866) -- (2.5, 0.866);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
        \fill (1.5, -0.5) node [below] {(a)};
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-1.0, 0.0) circle [radius = 0.1];
        \fill (-2.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (-1.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (-1.5, 0.866);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (-0.5, 0.866) -- (-1.0, 0.0);
        \draw [dashed] [red] (-1.5, 0.866) -- (-2.0, 0.0);
        \fill (-0.5, -0.5) node [below] {(b)};
      \end{tikzpicture}\\

      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-1.0, 0.0) circle [radius = 0.1];
        \fill (-2.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (-1.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (-1.5, 0.866);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
        \draw [dashed] [red] (-1.5, 0.866) -- (-2.0, 0.0);
        \fill (-0.5, -0.5) node [below] {(c)};
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-2.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (-1.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (-1.5, 0.866);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
        \draw [dashed] [red] (-1.5, 0.866) -- (-2.0, 0.0);
        \fill (-0.5, -0.5) node [below] {(d)};
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-1.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (-1.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (-1.5, 0.866);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
        \draw [dashed] [red] (-1.5, 0.866) -- (-1.0, 0.0);
        \fill (-0.5, -0.5) node [below] {(e)};
      \end{tikzpicture}\\

      (c) there is an inactive bead at (-1,0).\\
      (d) there is no bead at (-1,0).

    \end{tabular}
    \caption{}
    \label{fig:3bonds}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \begin{tabular}{ccc}
      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (2.0, 0.0) circle [radius = 0.1];
        \fill (3.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill [blue] (1.5, 0.866) circle [radius = 0.1];
        \fill [blue] (2.5, 0.866) circle [radius = 0.1];
        \fill [blue] (3.5, 0.866) circle [radius = 0.1];
        \draw [blue] (0.5, 0.866) -- (1.5, 0.866);
        \draw [blue] (1.5, 0.866) -- (2.5, 0.866);
        \draw [blue] (2.5, 0.866) -- (3.5, 0.866);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
        \draw [dashed] (3.5, -0.866) -- (3.0, 0.0);
        \draw [dashed] (0.5, 0.0) -- (3.0, 0.0);
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (2.0, 0.0) circle [radius = 0.1];
        \fill (3.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill [blue] (1.5, 0.866) circle [radius = 0.1];
        \fill [blue] (2.5, 0.866) circle [radius = 0.1];
        \fill [blue] (1.0, 1.732) circle [radius = 0.1];
        \draw [blue] (0.5, 0.866) -- (1.0, 1.732);
        \draw [blue] (1.5, 0.866) -- (1.0, 1.732);
        \draw [blue] (1.5, 0.866) -- (2.5, 0.866);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
        \draw [dashed] (3.5, -0.866) -- (3.0, 0.0);
        \draw [dashed] (0.5, 0.0) -- (3.0, 0.0);
      \end{tikzpicture}

    \end{tabular}
    \caption{}
    \label{fig:hexcorner}
  \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (1.5, 0.866) circle [radius = 0.1];
        \fill (1.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [left] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (1.5, 0.866);
        \draw (1.0, 1.732) -- (1.5, 0.866);
        \draw [dashed] [red] (1.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (1.0, 1.732) -- (0.5, 0.866);
        \draw [dashed] [red] (1.0, 1.732) -- (0.5, 0.866);
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (-0.5, 0.866) node [left] {$(0, 1)$};
        \draw (0.0, 0.0) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (0.5, 0.866);
        \draw (0.0, 1.732) -- (0.5, 0.866);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
      \end{tikzpicture}

    \end{tabular}
    \caption{}
    \label{fig:beadat(1,0)}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (0.0, 1.732) -- (-0.5, 0.866);
        \draw [dashed] [red] (0.0, 1.732) -- (0.5, 0.866);
        \draw [dashed] [red] (0.0, 0.0) -- (-0.5, 0.866);
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(1, 1)$};
        \draw (0.0, 0.0) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (0.5, 0.866);
        \draw (0.0, 1.732) -- (0.5, 0.866);
        \draw [dashed] [red] (0.0, 0.0) -- (0.5, 0.866);
        \draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
      \end{tikzpicture}

    \end{tabular}
    \caption{}
    \label{fig:beadi2}
  \end{center}
\end{figure}

@@

      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (2.0, 0.0) circle [radius = 0.1];
        \fill (3.0, 0.0) circle [radius = 0.1];
        \fill (4.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (1.5, 0.866) circle [radius = 0.1];
        \fill (2.5, 0.866) circle [radius = 0.1];
        \fill (3.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (1.5, 0.866);
        \draw (1.5, 0.866) -- (2.5, 0.866);
        \draw (2.5, 0.866) -- (3.5, 0.866);
        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
        \draw [dashed] [red] (3.5, 0.866) -- (4.0, 0.0);
        \fill (1.5, -0.5) node [below] {(a)};
      \end{tikzpicture}

>>>>

\begin{enumerate}
	\item bead $i+1$ is fixed at $(2,1)$ and can bond with a bead at $(2,0)$. Now consider bead $i+2$. For $i+1$ to be fixed at $(2,1)$, $i+2$ needs to form a bond somewhere, otherwise $i+2$ could go to $(2,1)$ forming the bond with the bead at $(2,0)$ and there would be two conformations with the maximal $1$ bond. The only possibility is that there is a bead at $(3,0)$ and $i+2$ can bond with it when placed at $(3,1)$. We can apply the same argument inductively: there is some $m\geq 0$ such that grid points $(\ell,0)$ are occupied by active beads, for all $\ell\in \{2,\dots,2+m\}$, and there is no bead at $(3+m,0)$. Such an $m$ exists, and it is not greater than $n$. Then, bead $i+\ell$ is fixed at $(\ell+1,1)$ and bonds with $(\ell+1,0)$. However, bead $i+2+m$ cannot be fixed anywhere, because $i+2+m$ and $i+3+m$ can only add one bond to the conformation, and that is possible either with $i+2+m \rightarrow (2+m,1)$, $i+3+m \rightarrow (3+m,1)$ or with $i+2+m \rightarrow (2+m,2)$, $i+3+m \rightarrow (2+m,1)$. 
	\begin{figure}
		\centering
		\includegraphics[width=0.9\linewidth]{./Fig/hexagonOut2}
		\caption{}
		\label{fig:hexagonout2}
	\end{figure}

@@

\begin{figure}
	\centering
	%\includegraphics[width=0.3\linewidth]{./hexagonOut1}
	%\hspace{10mm} %
	\includegraphics[width=0.8\linewidth]{./Fig/hexagonOut3n}

@@

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (0.0, 1.732) -- (-0.5, 0.866);
        \draw [dotted] [red] (0.0, 1.732) -- (0.5, 0.866);
        \draw [dotted] [red] (0.0, 0.0) -- (-0.5, 0.866);
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \draw (0.0, 0.0) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (0.5, 0.866);
        \draw (0.0, 1.732) -- (0.5, 0.866);
        \draw [dotted] [red] (0.0, 0.0) -- (0.5, 0.866);
        \draw [dotted] [red] (0.0, 1.732) -- (-0.5, 0.866);
      \end{tikzpicture}

    \end{tabular}
    \caption{Two conformations when a bead $i-1$ at (0,0) has a free hand}
    \label{fig:beadi}
  \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \begin{tabular}{ccc}
      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (2.0, 0.0) circle [radius = 0.1];
        \fill (3.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (1.5, 0.866) circle [radius = 0.1];
        \fill (2.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (1.5, 0.866);
        \draw (1.5, 0.866) -- (2.5, 0.866);
        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dotted] [red] (1.5, 0.866) -- (2.0, 0.0);
        \draw [dotted] [red] (2.5, 0.866) -- (3.0, 0.0);
        \fill (1.5, -0.5) node [below] {(a)};
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-1.0, 0.0) circle [radius = 0.1];
        \fill (-2.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (-1.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (-1.5, 0.866);
        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dotted] [red] (-0.5, 0.866) -- (-1.0, 0.0);
        \draw [dotted] [red] (-1.5, 0.866) -- (-2.0, 0.0);
        \fill (-0.5, -0.5) node [below] {(b)};
      \end{tikzpicture}\\

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-1.0, 0.0) circle [radius = 0.1];
        \fill (-2.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (-1.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (-1.5, 0.866);
        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dotted] [red] (-0.5, 0.866) -- (0.0, 0.0);
        \draw [dotted] [red] (-1.5, 0.866) -- (-2.0, 0.0);
        \fill (-0.5, -0.5) node [below] {(c)};
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-2.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (-1.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (-1.5, 0.866);
        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dotted] [red] (-0.5, 0.866) -- (0.0, 0.0);
        \draw [dotted] [red] (-1.5, 0.866) -- (-2.0, 0.0);
        \fill (-0.5, -0.5) node [below] {(d)};
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-1.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (-1.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (-1.5, 0.866);
        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dotted] [red] (-0.5, 0.866) -- (0.0, 0.0);
        \draw [dotted] [red] (-1.5, 0.866) -- (-1.0, 0.0);
        \fill (-0.5, -0.5) node [below] {(e)};
      \end{tikzpicture}\\

    \end{tabular}
    \caption{When beads $i, i+1, i+2$ make three hydrogen bonds \newline (c) there is an inactive bead at (-1,0). \newline (d) there is no bead at (-1,0).}
    \label{fig:3bonds}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \begin{tabular}{ccc}
      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (2.0, 0.0) circle [radius = 0.1];
        \fill (3.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill [blue] (1.5, 0.866) circle [radius = 0.1];
        \fill [blue] (2.5, 0.866) circle [radius = 0.1];
        \fill [blue] (3.5, 0.866) circle [radius = 0.1];
        \draw [blue] (0.5, 0.866) -- (1.5, 0.866);
        \draw [blue] (1.5, 0.866) -- (2.5, 0.866);
        \draw [blue] (2.5, 0.866) -- (3.5, 0.866);
        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dotted] [red] (1.5, 0.866) -- (2.0, 0.0);
        \draw [dotted] [red] (2.5, 0.866) -- (3.0, 0.0);
        \draw [dashed] (3.5, -0.866) -- (3.0, 0.0);
        \draw [dashed] (0.5, 0.0) -- (3.0, 0.0);
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (2.0, 0.0) circle [radius = 0.1];
        \fill (3.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill [blue] (1.5, 0.866) circle [radius = 0.1];
        \fill [blue] (2.5, 0.866) circle [radius = 0.1];
        \fill [blue] (1.0, 1.732) circle [radius = 0.1];
        \draw [blue] (0.5, 0.866) -- (1.0, 1.732);
        \draw [blue] (1.5, 0.866) -- (1.0, 1.732);
        \draw [blue] (1.5, 0.866) -- (2.5, 0.866);
        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dotted] [red] (1.5, 0.866) -- (2.0, 0.0);
        \draw [dotted] [red] (2.5, 0.866) -- (3.0, 0.0);
        \draw [dashed] (3.5, -0.866) -- (3.0, 0.0);
        \draw [dashed] (0.5, 0.0) -- (3.0, 0.0);
      \end{tikzpicture}

    \end{tabular}
    \caption{Being nondeterministic when reaching a corner of $\hexagon_p^n$}
    \label{fig:hexcorner}
  \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (1.5, 0.866) circle [radius = 0.1];
        \fill (1.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [left] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (1.5, 0.866);
        \draw (1.0, 1.732) -- (1.5, 0.866);
        \draw [dotted] [red] (1.5, 0.866) -- (1.0, 0.0);
        \draw [dotted] [red] (1.0, 1.732) -- (0.5, 0.866);
        \draw [dotted] [red] (1.0, 1.732) -- (0.5, 0.866);
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (-0.5, 0.866) node [left] {$(0, 1)$};
        \draw (0.0, 0.0) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (0.5, 0.866);
        \draw (0.0, 1.732) -- (0.5, 0.866);
        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dotted] [red] (0.0, 1.732) -- (-0.5, 0.866);
      \end{tikzpicture}

    \end{tabular}
    \caption{Two conformations when a bead at (1,0) has a free hand}
    \label{fig:beadat(1,0)}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (0.0, 1.732) -- (-0.5, 0.866);
        \draw [dotted] [red] (0.0, 1.732) -- (0.5, 0.866);
        \draw [dotted] [red] (0.0, 0.0) -- (-0.5, 0.866);
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(1, 1)$};
        \draw (0.0, 0.0) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (0.5, 0.866);
        \draw (0.0, 1.732) -- (0.5, 0.866);
        \draw [dotted] [red] (0.0, 0.0) -- (0.5, 0.866);
        \draw [dotted] [red] (0.0, 1.732) -- (-0.5, 0.866);
      \end{tikzpicture}

    \end{tabular}
    \caption{Two conformations when a bead $i$ at (1,1) has a free hand}
    \label{fig:beadi2}
  \end{center}
\end{figure}

@@

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (2.0, 0.0) circle [radius = 0.1];
        \fill (3.0, 0.0) circle [radius = 0.1];
        \fill (4.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (1.5, 0.866) circle [radius = 0.1];
        \fill (2.5, 0.866) circle [radius = 0.1];
        \fill (3.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (1.5, 0.866);
        \draw (1.5, 0.866) -- (2.5, 0.866);
        \draw (2.5, 0.866) -- (3.5, 0.866);
        \draw [dotted] [red] (1.5, 0.866) -- (2.0, 0.0);
        \draw [dotted] [red] (2.5, 0.866) -- (3.0, 0.0);
        \draw [dotted] [red] (3.5, 0.866) -- (4.0, 0.0);
        \fill (1.5, -0.5) node [below] {(a)};
      \end{tikzpicture}
